Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-24 trunk/constantRate/ConstCompFuzzExt-reorg.tex
working on reusability

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

@@

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$). \onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph. Consider ignoring them here.}
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source. \bnote{negative results stated in our contributions. keep there?}

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure\onote{consider adding here that the class of sources we can deal with (in all constructions) contains many natural sources (or something along these lines).}.  Table~\ref{tab:upper bounds} summarizes our constructions. \lnote{Note sure about the first line of this table. What does ``exploit distribution structure'' mean? Also, can we make it look a bit better? Perhaps center. Perhaps also remove some lines. Perhaps make "main feature" column the same part of speech in each entry.}
\onote{The table is confusing to me: all the constructions exploits distribution structure. In the second construction most symbols must contribute fresh entropy as well. Third construction is also reusable. Perhaps there is a better way to organize this information.}
\bnote{these comments are all valid.  I'm not sure what to do about it.  Maybe organize by techniques and then notes (for limitations and features?)}
Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols. %It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

We switch to computational security to obtain constructions with additional features. Our second construction provides reusability (against computationally bounded adversaries).  Like the first construction,
it requires that a constant fraction of symbols contribute fresh entropy. However,
the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution. The switch to computational security is necessary here: as discussed in \secref{sec:reusable}, it is impossible to obtain such reusability information-theoretically for sources with more errors than entropy.
This construction requires that the fraction of errors is subconstant.

@@

\begin{table}
\begin{tabular}{l | l | l | l }
Construction & Security & Main Feature & Main Limitation \\
\hline
\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
&&structure & fresh entropy \\\hline
\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
&& & error tolerance\\\hline
\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
& &  symbols & size symbols
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
\label{tab:upper bounds}
\end{table}

@@

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.

Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).  Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).
Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups. Boyen transforms this construction to insider security using random oracles. In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.  Unfortunately, this class of correlation is relatively weak and unrealistic.
%\paragraph{Previous Negative Results}

Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.
However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.  If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
%\bnote{old stuff}
%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.
%
%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

To overcome this result, we consider computationally bounded adversaries.
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
We modify the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss the differences in \apref{sec:comparing reusability}.

\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{enumerate}%[leftmargin=-.6in]
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{enumerate}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\subsection{Defining Reusability in the Computational Setting}
\label{sec:comparing reusability}

The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to require the entire adversary to be computationally bounded.  Our construction satisfies this alternative adaption as well.}

Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.

Finally, we allow the distinguishing adversary to see other keys.  This is strictly stronger than the definition of Boyen.  However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.  This is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.  Our reusable construction~(\consref{cons:sampling}) is not insider secure.

@@

%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.  %Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.  Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.  Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.  In order to provide any meaningful security guarantee, the source distribution must be restricted.  See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
\section{Characterizing unguessable block distributions}
\label{sec:characterize}

\defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.  In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).  We first show some sources that are unguessable block distributions~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block distributions~(\secref{sec:negative ex}).

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block distribution.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block distribution.
\end{claim}
\begin{proof}
It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $j$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
&=\Hoo(W_j) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

\begin{claim}
\label{cl:each block from single seed}
Let $f:\zo^e \rightarrow \mathcal{Z}^\gamma$ be a function.  Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.  If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block distribution.
\end{claim}
\begin{proof}
Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.  Consider a query $q_k$ on block $j$.  There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$. Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.  Then the possible responses are strings with Hamming weight at most $1$ (like in the
proof of \clref{cl:independent high ent}),
 and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $j$, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_j) -\log (q+1)$.
\end{proof}

@@

If an adversary can learn blocks in succession they can eventually recover the entire secret.  In order for a distribution to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.  This translates to having a super-logarithmic jump early enough.

>>>>

\begin{abstract}
\lnote{needs work}
Fuzzy extractors convert a noisy source of entropy into the same uniformly distributed key~(Dodis et al., Eurocrypt 2004).  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of tolerated error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for every source with this property.  Most known approaches for building fuzzy extractors work in the worst case and thus cannot be used when a source has \emph{more errors than entropy}.

@@

\item \textbf{Computational}
%By adding computational techniques we obtain constructions with additional features.  
Our second construction is also secure when each symbol contributes fresh entropy.  
Additionally, it is a reusable fuzzy extractor~(Boyen, CCS 2004).  A reusable fuzzy extractor allows multiple readings of the source to be enrolled securely.  Our construction is reusable if each individual reading is a supported source.  Previous reusable fuzzy extractors required the correlation between repeated readings to be drawn from a small and unrealistic class.  This construction corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

@@

Fuzzy extractors consist of a pair of algorithms: \gen (used once, at ``enrollment'') takes a source value $w$, and produces a key $r$ and a public helper value $p$.  The second algorithm \rep (used subsequently) takes this helper value $p$ and a close $w'$ to reproduce the original key $r$.
The correctness guarantee is that $r$ will be correctly reproduced by \rep as long as $w'$ is no farther than $t$ from $w$ in some metric space.% (in this paper, we focus on the Hamming metric on length $\gamma$ strings over some alphabet $\mathcal{Z}$). \onote{parameters $\gamma$ and $\mathcal{Z}$ are not used until they are reintroduced in our contribution paragraph. Consider ignoring them here.}
 The security guarantee is that $r$ produced by \gen is close to uniform (information-theoretically \cite{DBLP:journals/siamcomp/DodisORS08} or computationally \cite{fuller2013computational}), even given $p$. This guarantee holds as long as $w$ comes from a high-quality distribution, which
traditionally has been defined as \emph{any} distribution with sufficient min-entropy $m$.

@@

The situation with reusability is even worse: the only known construction of reusable fuzzy extractors \cite{Boyen2004} requires very particular relationships between $w_i$ values, which are unlikely to hold in any practical source.

\paragraph{Our Contributions}
We provide the first constructions of fuzzy extractors that can be used for large classes of sources that have more errors than entropy.  Our constructions work for Hamming errors for strings $w$ of length $\gamma$ over some alphabet $\mathcal{Z}$. Naturally, as argued above, these constructions cannot work for all sources of a given entropy; each construction comes with a constraint on the sources for which it is secure.  Table~\ref{tab:upper bounds} summarizes our constructions. \bnote{table better?}
Our first construction provides information-theoretic security.  It can correct a constant fraction of errors, but requires that a constant fraction of the symbols contribute fresh entropy, even conditioned on previous symbols~(\defref{def:partial source}). %It requires an alphabet size that is super constant in the security parameter. \lnote{keep this last sentence?}

We switch to computational security to obtain constructions with additional features. Our second construction provides reusability (against computationally bounded adversaries).  Like the first construction,
it requires that a constant fraction of symbols contribute fresh entropy. However,
the reusability we obtain is very strong:  security holds even if the multiple readings $w_i$ used in $\gen$ are \emph{arbitrarily correlated}, as long as each $w_i$ \emph{individually} satisfies the above conditions as a distribution. 
This construction requires that the fraction of errors is subconstant.

@@

\begin{table}
\begin{tabular}{l l l c c}
 & Security & Source Structure & Error-Tolerance & Alphabet Size\\
\hline
\consref{cons:info theoretic} & Info-theoretic  & Partial block source& $\Theta(\gamma)$ & $\omega(1)$ \\
\consref{cons:sampling} & Reusable Computational & Partial block source& $o(\gamma)$ & $\omega(1)$ \\
\consref{cons:first construction} & Computational & Unguessable block source & $\Theta(\gamma)$ & $n^{\omega(1)}$
\end{tabular}
\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.  Partial blocks sources are defined in \defref{def:partial source} and unguessable block sources are defined in \defref{def:block guessable}.}
\label{tab:upper bounds}
\end{table}

%\begin{table}
%\begin{tabular}{l | l | l | l }
%Construction & Security & Main Feature  & Main Limitations \\
%\hline
%\consref{cons:info theoretic} & Info-theoretic & Exploit distribution & Symbols must add\\
%&&structure & fresh entropy \\\hline
%\consref{cons:sampling} & Computational  & Reusability & Sub-constant fraction \\
%&& & error tolerance\\\hline
%\consref{cons:first construction} & Computational & Allows correlated & Super-polynomial \\
%& &  symbols & size symbols
%\end{tabular}
%\caption{Summary of new constructions.  All constructions support families of distributions with more errors than entropy.}
%\label{tab:upper bounds}
%\end{table}

@@

An additional desirable feature of fuzzy extractors is reusability~\cite{Boyen2004}. Inuitively, it is the ability to support multiple independent enrollments of the same value, allowing users to reuse the same biometric or PUF, for example, with multiple noncommunicating providers. More precisely, the algorithm $\gen$ may be run multiple times on correlated readings $w_1,..., w_q$ of a given source. Each time, $\gen$ will produce a different pair of values $(r_1, p_1),..., (r_q, p_q)$. Security for each extracted string $r_i$ should hold even in the presence of all the helper strings $p_1, \dots, p_q$ (the reproduction procedure $\rep$ at the $i$th provider still obtains only a single $w'_i$ close to $w_i$ and uses a single helper string $p_i$). Because the multiple providers may not trust each other, a stronger security feature (which we satisfy) ensures that each $r_i$ is secure even when all $r_j$ for $j\neq i$ are also given to the adversary.

 Our ability to construct reusable fuzzy extractors depends on the types of correlations allowed among $w_1, \dots, w_q$. Boyen \cite{Boyen2004} showed how to do so when each $w_i$ is a shift of $w_1$ by a value that is oblivious to the value of $w_1$ itself (formally, $w_i$ is a result of a transitive isometry applied to $w_1$). Boyen also showed that even for this weak class of correlations, any secure sketch must lose at least $\log |B_t|$ entropy~\cite[Theorem 11]{Boyen2004}.

%\paragraph{Previous Negative Results}

%\bnote{old stuff}
%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.
%
%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

%To overcome this result, we consider computationally bounded adversaries.
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
We modify the definition of Boyen~\cite[Definition 6]{Boyen2004} for the computational setting.  We discuss the our definition and definitions due to Boyen in \apref{sec:comparing reusability}.

\begin{definition}[Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{itemize}%[leftmargin=-.6in]
\item \textbf{Sampling} The challenger samples $w_1\leftarrow W_1$.
\item \textbf{Perturbation} For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.\bnote{should we allow keys to the perturbation adversary?}
\item \textbf{Distinguishing} The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{itemize}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\subsection{Reusability Fuzzy Extractors}
\label{sec:comparing reusability}

The goal of a reusable fuzzy extractor is to allow enrollment of a source across multiple services.  A service $i$ sees an reading of the source $w_i$.
Boyen considers two versions of reusable fuzzy extractors, first where the adversary sees $p_1,..., p_q$~(outsider security~\cite[Definition 6]{Boyen2004}) and tries to learn about the values $w_1,..., w_q$ or the keys $r_1,..., r_q$.  Second, where the adversary controls some subset of the servers and can key generation on arbitrary $p_i'$~(insider security~\cite[Definition 7]{Boyen2004}).   This allows the adversary to learn a subset of keys $r_i$~(by performing key generation on the valid $p_i$).  This definition makes sense when servers are compromised~(after enrollment) and act maliciously.  In both definitions, the adversary creates a perturbation function $_i$ after seeing $p_1,..., p_{i-1}$~(and generated keys for outsider security) and the challenger generates $w_i = f_i(w_1)$.  The definition is parameterized by the class of allowed perturbation functions.

Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the perturbation family is a transitive isometric permutation groups. Boyen transforms this construction to insider security using random oracles. %In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.

Insider security strengthens outsider security in two ways.  First, it allows the adversary to see some subset of keys, second it allows the adversary to perform key generation on arbitrary $p_i$.  This mixes two properties of a fuzzy extractor:  reusability and robustness~\cite{dkrs2006}.  Robust fuzzy extractors provide security against modified $p$.  
In this work, we show reusability when $r_i$ are observed but do not handle the issue of robustness.  That is, we assume keys may be exposed but servers keep honest state.  Our definition lies between outsider and insider security.

We adapt the definition of Boyen to the computational setting~(\defref{def:outsider fuzz ext}).  
The definition of Boyen considers a single adversary.  We split the adversary into two parts, one of which is information-theoretic and another that is computationally bounded.  The functions $f_2,..., f_q$ can be thought of as a single adversary that sees all prior state.  However, to provide meaningful security in the computational setting, we cannot have communication between these adversaries.\footnote{An alternative would be to have a single computationally bounded adversary.  Our construction satisfies this alternative adaption as well.}
Because these two adversaries do not communicate we strengthen the definition by allowing the perturbation adversary~($f_i$) to see the original sample $w_1$.  This was not allowed in the definition of Boyen as it would make security impossible.

%Finally, we allow the distinguishing adversary to see other keys \lnote{we do? then why do we call our definition ``outsider''?}.  This is strictly stronger than the definition of Boyen \lnote{you mean than the outsider security definition of Boyen?}.  However, it is weaker than the notion of insider reusable fuzzy extractors where the adversary sees key generation on arbitrary $p$.  This \lnote{what is ``this''?} is a mixture of reusability and robustness~\cite{dkrs2006} of the fuzzy extractor.  Our reusable construction~(\consref{cons:sampling}) is not insider secure \lnote{according to Boyen's notion, right? Why not say ``not robust'' and/or clarify that $r_i$ can leak but $p_i$ cannot be modified.}.

@@

%\consref{cons:sampling} is the fuzzy extractor that allows for arbitrary correlation between $w_1,..., w_q$ as long as each $w_i$ comes from an admissible distribution.  %Our construction can be made secure information-theoretically for fixed values of $q$ or computationally for an arbitrary value $q = \poly(n)$.  Our construction is based on a modification of the computational fuzzy extractor of Canetti et al.~\cite[Construction 5.2]{canetti2014key}.  Their construction is secure for a restricted class of distributions.\footnote{This is necessary as they secure distributions with more errors than entropy.  In order to provide any meaningful security guarantee, the source distribution must be restricted.  See the introduction of~\cite{canetti2014key} for discussion.}  In addition to showing the reusability of their construction, we provide two significant improvements:
\section{Characterizing unguessable block sources}
\label{sec:characterize}

\defref{def:block guessable} is an inherently adaptive definition and a little unwieldy.  In this section, we partially characterize sources that satisfy \defref{def:block guessable}.
The majority of the difficulty in characterizing \defref{def:block guessable} is that different blocks may be dependent, so an equality query on block $i$ may reshape the distribution of block $j$.  In the examples that follow we denote the adversary by $S$ as we consider security against computationally unbounded adversaries defined in VGB obfuscation~(\defref{def:obf}).  We first show some sources that are unguessable block sources~(\secref{sec:positive ex}) and then show distributions with high overall entropy that are not unguessable block sources~(\secref{sec:negative ex}).

@@

\begin{claim}
\label{cl:independent high ent}
Let $W = W_1,  ... , W_\gamma$ be a source in which all blocks $W_j$  are mutually independent.  Let $\alpha$ be a parameter.  Let $J\subset \{1,..., \gamma\}$ be a set of indices such that for all $j\in J$, $\Hoo(W_j ) =\alpha $.  Then for any $q$, $W$ is a $(q, \alpha - \log (q+1), \gamma - |J|)$-unguessable block source.  In particular, when $\alpha = \omega(\log n)$ and $q = \poly(n)$, then $W$ is a $(q, \omega(\log n), \gamma - |J|)$-unguessable block source.
\end{claim}
\begin{proof}
It suffices to show that for all $j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}) = \alpha -\log (q+1)$.
We can ignore queries for all blocks but the $j$th, as the blocks are independent. Furthermore, without loss of generality, we can assume that no duplicate queries are asked, and that the adversary is deterministic ($S$ can calculate the best coins). Let $A_1, A_2, \dots A_q$ be the random variables representing the oracle answers for an  adversary $S$ making $q$  queries about the $i$th block. Each $A_k$ is just a bit, and at most one of them  is equal to 1 (because duplicate queries are disallowed). Thus, the total number of possible responses is $q+1$. Thus, we have the following,
\begin{align*}
\Hav(W_j | View(S^{\mathcal{O}_{W}(\cdot, \cdot)}) &= \Hav(W_j| A_1, \dots, A_q)\\
&=\Hoo(W_j) - |A_1, \dots, A_q|\\
&=\alpha - \log (q+1)\,,
\end{align*}
where the second line follows from the first by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}.
\end{proof}
\noindent In their work on computational fuzzy extractors, Fuller, Meng, and Reyzin~\cite{fuller2013computational} show a construction for block-fixing sources, where each block is either uniform or a fixed symbol~(block fixing sources were introduced by Kamp and Zuckerman~\cite{KZ07}).  \clref{cl:independent high ent} shows that \defref{def:block guessable} captures, in particular, this class of distributions.
However, \defref{def:block guessable} captures more distributions.  We now consider more complicated distributions where blocks are not independent.

\begin{claim}
\label{cl:each block from single seed}
Let $f:\zo^e \rightarrow \mathcal{Z}^\gamma$ be a function.  Furthermore, let $f_j$ denote the restriction of $f$'s output to its $j$th coordinate.  If for all $j$, $f_j$ is injective then $W = f(U_e)$ is a $( q, e - \log (q+1), 0)$-unguessable block source.
\end{claim}
\begin{proof}
Since $f$ is injective on each block, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) = \Hav(U_e | View(S^{I_{W}(\cdot, \cdot)}))$.  Consider a query $q_k$ on block $j$.  There are two possibilities: either $q_k$ is not in the image of $f_j$,  or $q_k$ can be considered a query on the preimage $f_j^{-1}(q_k)$. Then (by assuming $S$ knows $f$) we can eliminate queries which correspond to the same value of $U_e$.  Then the possible responses are strings with Hamming weight at most $1$ (like in the
proof of \clref{cl:independent high ent}),
 and by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08} we have for all $j$, $\Hav(W_j | View(S^{I_{W}(\cdot, \cdot)})) \geq \Hoo(W_j) -\log (q+1)$.
\end{proof}

@@

If an adversary can learn blocks in succession they can eventually recover the entire secret.  In order for a source to be block unguessable the adversary must get ``stuck'' early enough in their recovery process.  This translates to having a super-logarithmic jump early enough.
